--- 
title: "A Minimal Book Example"
author: "Yihui Xie"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

<!--chapter:end:index.Rmd-->

# System Administrators {#sysadmins}

## Server Software

- https://github.com/mhk-env/mhk-env_server-software


Symbolically link (`ln -s`) a Shiny server app from within the Github repo (`mhk-env_shiny-apps`) to the active folder `/srv/shiny-server` from where Shiny apps get served:

```
ln -s /share/github/mhk-env_shiny-apps/report-gen2 /srv/shiny-server/report
```

## OLD (bookdown)

This website describes how to use open-source software and data to construct the [MarineEnergy.app](https://MarineEnergy.app) Toolkit for Enviromental Compliance, organized for now by audience.

<!--chapter:end:01-sysadmins.Rmd-->

# R Technicians {#rtech}

## Updating dynamic content

- [Interactions]: re-knit env.Rmd.

### Shiny App Content Updates
To render changes made to content in a Shiny app, navigate to the folder that contains the application files to run the app. Shiny apps are served from a standard folder where they are symbolically linked to source files. These folders contain the global.R, ui.R, server.R scripts that run the app.

- global.R: functions used in ui.R and server.R can be defined here, sourced here from other files or in loaded libraries
- ui.R: defines the user interface, or display, of the contents in the shiny app; this is navigable through the bookmarks in the lower left menu of the Code panel in RStudio
- server.R: back-end server functions to populate the user interface; this is also navigable through the bookmarks in the lower left menu of the Code panel in RStudio


### Projects Page

The projects page is accessed from the marineenergy.app Reporting Tool. Projects shown on the map and timeline diagram are updated periodically based on input from stakeholders. The content is updated through a series of steps as outlined below.

- Enter new project information into: [data | marineenergy.app - Google Sheet](https://docs.google.com/spreadsheets/d/1MTlWQgBeV4eNbM2JXNXU3Y-_Y6QcOOfjWFyKWfdMIQM/edit?usp=sharing)
    - If a new project permit type is needed, add this to the list presented on the project_permit_types worksheet
- Use RStudio to open the apps_dev/scripts/update_all.R script within the /share/github/apps_dev repository branch
    - Run the update_projects() function
        - Note that this function is defined in the apps_dev/scripts/update.R script
- Commit changes


<!--chapter:end:02-rtech.Rmd-->

# Community Members {#comm}

## Edit in OpenEI

- [Regulations](https://marineenergy.app/regs.html) 
  * [MarineEnergyApp | OpenEI](https://openei.org/wiki/MarineEnergyApp)

## Suggest in Google Sheets

Suggest and then get reviewed by R-technicians for updating.

- [Projects](https://marineenergy.app/projects.html)
  * [projects](https://docs.google.com/spreadsheets/d/1HC5hXyi2RQSHevnV7rvyk748U5-X3iUw70ewHEfrHm0/edit#gid=793817660)
- [Documents](https://marineenergy.app/ferc.html)
  * [documents](https://docs.google.com/spreadsheets/d/1c9pFSkQyQvLFpyMT4KlBoSFA_wtJ_iNj8YmNX_RZmXc/edit#gid=951079264)
- [Spatial ](https://shiny.marineenergy.app/report/?nav=Spatial)
  * [spatial](https://docs.google.com/spreadsheets/d/1MMVqPr39R5gAyZdY2iJIkkIdYqgEBJYQeGqDk1z-RKQ/edit#gid=936111013)


<!--chapter:end:03-community.Rmd-->

# Applications

Some _significant_ applications are demonstrated in this chapter.

## Example one

## Example two

<!--chapter:end:04-application.Rmd-->

# Final Words

We have finished a nice book.

<!--chapter:end:05-summary.Rmd-->

`r if (knitr:::is_html_output()) '
# References {-}
'`

<!--chapter:end:06-references.Rmd-->

