# Welcome

## How to use the help documentation:
This help documentation is organized by role, including System Administrators (sysadmins), RShiny Application developers (rtech), and community users (community). Information related to corresponding workflows are located in each section of the help documentation. 

For information related to server setup and location please refer to the sysadmins section of the documentation. For application development methods and existing workflows to update the application please refer to the rtech section of the help. In order to understand how to contribute to the application as a part of the user community please refer to the community section of the documentation.

## Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
